A Bayesian Framework for Learning Regular Expressions

### 2012-12-08 paper/paper.tex
catchup; adding to conclusion

% 
% Annual Cognitive Science Conference Format

@@

\subsection{Generating Hypotheses}
The hypothesis space is initiated with the base hypothesis, the term applied to a DFA that accepts strictly the input strings. We begin generating a series of consecutive states, where the transition between the first state and the second state is governed by the first letter of the first string, the transition between the second and the third is governend by the the second letter, and so on. For each additional string, if the first i characters overlap with those of any of the first i characters of one previous string but differ in the $i+1$th, we add no new states to the DFA until the transition between the i-1th state and the ith state. We then generate new states for the remaining characters of the string. See Figure~\ref{base_hypothesis} for an example of the first hypothesis generated from a set $S = $\{\verb!ababb!, \verb!abbab!\} .
  \begin{figure}[ht]
\begin{center}
\begin{align*}
\includegraphics[scale=0.4]{readin.png}
\end{align*}
\end{center}
\caption{An example base hypothesis DFA generated from the strings `ababb' and `abbab'. Note that the two strings share the first two states, but that the fifth and tenth are distinct.} 
\label{base_hypothesis}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\begin{align*}
\includegraphics[scale=0.6]{results.png}
\end{align*}
\end{center}
\caption{Chart showing  $p(s \in \mathcal{L} | S \subseteq {L}) $. Human subject data is in red, model data is in blue. $R$ = .75} 
\label{results-chart}
\end{figure}

We note that subjects completed the 10 or 11 question survey on average in around three minutes. It remains unclear if more standardized results would have emerged in certain cases if subjects had taken more time with the task. In addition, more fine grained results may have been obtained if we had instead allowed users to bet certain amounts on whether or not a test string was in $S$.

We note that in cases 1 (S = \{\verb!yyyt!, \verb!yt!, \verb!yyyt!, \verb!yyyt!, \verb!yt!\}, s= \verb!yyyyyt!), 4 (S = \{\verb!jojojojo!, \verb!jojojojo!, \verb!jojojojo!\}, s = \verb!jojo!), and 6 (S = \{\verb!twtwtw!, \verb!twtwtw!, \verb!twtwtw!\}, s =  \verb!tw!), it is clear that the model weighs a smaller number of transitions greater than human subjects do. However, because this same parameter in part controls for wildcards, lowering it reduces performance on many other cases. This suggests that our model's parameter $\beta$ may in fact be better represented by more than one variable in human decision making.

@@

% \section{General Formatting Instructions}

% For standard spoken papers and standard posters, the entire contribution (including figures, references, everything) can be no longer than six pages. For abstract posters, the entire contribution can be no longer than one page. For symposia, the entire contribution can be no longer than two pages.

% The text of the paper should be formatted in two columns with an
% overall width of 7 inches (17.8 cm) and length of 9.25 inches (23.5
% cm), with 0.25 inches between the columns. Leave two line spaces
% between the last author listed and the text of the paper. The left
% margin should be 0.75 inches and the top margin should be 1 inch.
% \textbf{The right and bottom margins will depend on whether you use
%   U.S. letter or A4 paper, so you must be sure to measure the width of
%   the printed text.} Use 10~point Times Roman with 12~point vertical
% spacing, unless otherwise specified.

% The title should be in 14~point, bold, and centered. The title should
% be formatted with initial caps (the first letter of content words
% capitalized and the rest lower case). Each author's name should appear
% on a separate line, 11~point bold, and centered, with the author's
% email address in parentheses. Under each author's name list the
% author's affiliation and postal address in ordinary 10~point type.

% Indent the first line of each paragraph by 1/8~inch (except for the
% first paragraph of a new section). Do not add extra vertical space
% between paragraphs.

% \section{First-Level Headings}

% First level headings should be in 12~point, initial caps, bold and
% centered. Leave one line space above the heading and 1/4~ line space
% below the heading.

% \subsection{Second-Level Headings}

% Second level headings should be 11~point, initial caps, bold, and
% flush left. Leave one line space above the heading and 1/4~ line
% space below the heading.

% \subsubsection{Third-Level Headings}

% Third-level headings should be 10~point, initial caps, bold, and flush
% left. Leave one line space above the heading, but no space after the
% heading.

% \section{Formalities, Footnotes, and Floats}

% Use standard APA citation format. Citations within the text should
% include the author's last name and year. If the authors' names are
% included in the sentence, place only the year in parentheses, as in
% \citeA{NewellSimon1972a}, but otherwise place the entire reference in
% parentheses with the authors and year separated by a comma
% \cite{NewellSimon1972a}. List multiple references alphabetically and
% separate them by semicolons
% \cite{ChalnickBillman1988a,NewellSimon1972a}. Use the
% et~al. construction only after listing all the authors to a
% publication in an earlier reference and for citations with four or
% more authors.

% \subsection{Footnotes}

% Indicate footnotes with a number\footnote{Sample of the first
%   footnote.} in the text. Place the footnotes in 9~point type at the
% bottom of the page on which they appear. Precede the footnote with a
% horizontal rule.\footnote{Sample of the second footnote.}

% \subsection{Tables}

% Number tables consecutively; place the table number and title (in
% 10~point) above the table with one line space above the caption and
% one line space below it, as in Table~\ref{sample-table}. You may float
% tables to the top or bottom of a column, set wide tables across both
% columns.

% \begin{table}[!ht]
% \begin{center} 
% \caption{Sample table title.} 
% \label{sample-table} 
% \vskip 0.12in
% \begin{tabular}{ll} 
% \hline
% Error type    &  Example \\
% \hline
% Take smaller        &   63 - 44 = 21 \\
% Always borrow~~~~   &   96 - 42 = 34 \\
% 0 - N = N           &   70 - 47 = 37 \\
% 0 - N = 0           &   70 - 47 = 30 \\
% \hline
% \end{tabular} 
% \end{center} 
% \end{table}

% \subsection{Figures}

% All artwork must be very dark for purposes of reproduction and should
% not be hand drawn. Number figures sequentially, placing the figure
% number and caption, in 10~point, after the figure with one line space
% above the caption and one line space below it, as in
% Figure~\ref{sample-figure}. If necessary, leave extra white space at
% the bottom of the page to avoid splitting the figure and figure
% caption. You may float figures to the top or bottom of a column, or
% set wide figures across both columns.

% \begin{figure}[ht]
% \begin{center}
% \fbox{CoGNiTiVe ScIeNcE}
% \end{center}
% \caption{This is a figure.} 
% \label{sample-figure}
% \end{figure}

% \section{Acknowledgments}

% Place acknowledgments (including funding information) in a section at
% the end of the paper.

% \section{References Instructions}

% Follow the APA Publication Manual for citation format, both within the
% text and in the reference list, with the following exceptions: (a) do
% not cite the page numbers of any book, including chapters in edited
% volumes; (b) use the same format for unpublished references as for
% published ones. Alphabetize references by the surnames of the authors,
% with single author entries preceding multiple author entries. Order
% references by the same authors by the year of publication, with the
% earliest first.

% Use a first level section heading for the reference list. Use a
% hanging indent style, with the first line of the reference flush
% against the left margin and subsequent lines indented by 1/8~inch.
% Below are example references for a conference paper, book chapter,
% journal article, technical report, dissertation, book, and edited
% volume, respectively.

\bibliographystyle{apacite}
\setlength{\bibleftmargin}{.125in}
\setlength{\bibindent}{-\bibleftmargin}
 \bibliography{regexbib}

>>>>

% Annual Cognitive Science Conference Format

@@

\subsection{Generating Hypotheses}
The hypothesis space is initiated with the base hypothesis, the term applied to a DFA that accepts strictly the input strings. We begin generating a series of consecutive states, where the transition between the first state and the second state is governed by the first letter of the first string, the transition between the second and the third is governend by the the second letter, and so on. For each additional string, if the first i characters overlap with those of any of the first i characters of one previous string but differ in the $i+1$th, we add no new states to the DFA until the transition between the i-1th state and the ith state. We then generate new states for the remaining characters of the string. See Figure~\ref{base_hypothesis} for an example of the first hypothesis generated from a set $S = $\{\verb!ababb!, \verb!abbab!\} .
  \begin{figure}[ht]
\begin{center}
\includegraphics[scale=0.4]{base_hypothesis.png}
\end{center}
\caption{An example base hypothesis DFA generated from the strings `ababb' and `abbab'. Note that the two strings share the first two states, but that the fifth and tenth are distinct.} 
\label{base_hypothesis}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\begin{align*}
\includegraphics[scale=0.5]{results.png}
\end{align*}
\end{center}
\caption{Chart showing  $p(s \in \mathcal{L} | S \subseteq {L}) $. Human subject data is in red, model data is in blue. $R$ = .75} 
\label{results-chart}
\end{figure}

Regarding our experimental data, we note that subjects completed the 10 or 11 question survey on average in around three minutes. It remains unclear if more standardized results would have emerged in certain cases if subjects had taken more time with the task. In addition, more fine grained results may have been obtained if we had instead allowed users to bet certain amounts on whether or not a test string was in $S$.

Observe that the model's performence is effectively all or none. In twelve of the trials, the model's predictions for  $p(s \in \mathcal{L} | S \subseteq {L}) $ was either 0 or 1.

We note that in cases 16 (S = \{\verb!yyyt!, \verb!yt!, \verb!yyyt!, \verb!yyyt!, \verb!yt!\}, s= \verb!yyyyyt!), 17 (S = \{\verb!jojojojo!, \verb!jojojojo!, \verb!jojojojo!\}, s = \verb!jojo!), and 18 (S = \{\verb!twtwtw!, \verb!twtwtw!, \verb!twtwtw!\}, s =  \verb!tw!), it is clear that the model weighs a smaller number of transitions greater than human subjects do. However, because this same parameter in part controls for wildcards, lowering it reduces performance on many other cases. This suggests that our model's parameter $\beta$ may in fact be better represented by more than one variable in human decision making.

@@

\bibliographystyle{apacite}
\setlength{\bibleftmargin}{.125in}
\setlength{\bibindent}{-\bibleftmargin}
 \bibliography{regbib}
